---
title: "Editing and Imputation"
author: "Vinayak Anand-Kumar"
date: "1/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Editing and imputing refer to changing erroneous data and filling in missing data respectively. This document addresses the following questions:
1) Why do we edit and impute data?
2) What does editing and imputation look like?

## Why do we edit and impute data?
The rationale for editing and imputing data is highlighted by presenting the challenges in data collection, how these can influence the quality of the statistical product, and introducing editing and imputing as a means of managing the impact of these data collection issues on quality.

### Perfect data vs. Actual data
In statistics, data is collected from units, which are commonly individuals, households or businesses. These collection units will provide values for a range of items/ variables. The purpose of data collection is to answer a question about a target population and target concept. As a result, it is intended that units and variables in the dataset are representative of the target population and target concept respectively.
The perfect dataset is one where the design has captured a representative set of units, the variables have mapped out the target concept accurately, and all units have responded to all items in the collection instrument correctly. With a perfect dataset, the researcher can make accurate inferences about the target population and concept, and in turn answer the question that prompted the data collection.
In reality there are challenges in data collection, which impede the ability to capture a target population and concept. The representativeness of the target population and the measurement of the target concept can be impacted by:
Including units outside the target population
Excluding units in the target population
Using variables that do not map onto the target concept
Missingness
Erroneous responses
The issues that arise in data collection will produce an answer to the research question that is further away from the “truth”.




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
